Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-07 ms.Rmd
Adding Wald tests, but not sure they are working correct

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC <- clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

  # Interaction needed? No
    anova(CourtshipAC_inter, CourtshipAC)

@@

  # Fit main effect model
      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)
      anova(CourtshipCC)

  # Test whether interaction is supported
    anova(CourtshipCC_inter, CourtshipCC)

>>>>

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC <- clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")
      robust_DispBgrdCC_inter <- clubSandwich::coef_test(DispBgrdCC_inter, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

  # Wald test of interaction
    background_AC_Court <- Wald_test(CourtshipAC_inter, constraints = constrain_zero(4), 
                                  cluster = CourtshipBgrd$ID, vcov = "CR2")

@@

  # Fit main effect model
      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)

    # Wald test of interaction
    inter_AC_Court <- Wald_test(CourtshipCC_inter, constraints = constrain_zero(4), 
                                  cluster = CourtshipBgrd$ID, vcov = "CR2")
